### 2023-04-06 chapter2/chapter2.tex
Updated substitution figure caption

\section{Results}
\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/substitution.png}
\centering
\caption{\textbf{Amino acid substitution models fit to disorder and order regions.}
\textbf{(A)} Amino acid state frequencies of substitution models. Amino acid symbols are ordered by their enrichment in disorder regions, calculated as the disorder-to-order ratio of their frequencies. Error bars represent standard deviations over models fit to different meta-alignments ($n = 25$). \textbf{(B)} $\log_{10}$ disorder-to-order ratios of exchangeability coefficients. \textbf{(C)} $\log_{10}$ disorder-to-order ratios of rate coefficients. The vertical and horizontal axes indicate the initial and target amino acids, respectively.}
\label{fig:substitution}
\end{figure}

>>>>

\section{Results}
\begin{figure}[h!]
\includegraphics[width=\textwidth]{substitution/out/substitution.png}
\centering
\caption{\textbf{Amino acid substitution models fit to disorder and order regions.}
\textbf{(A)} Amino acid frequencies of substitution models. Amino acid symbols are ordered by their enrichment in disorder regions, calculated as the disorder-to-order ratio of their frequencies. Error bars represent standard deviations over models fit to different meta-alignments ($n = 25$). \textbf{(B-C)} Exchangeability coefficients of disorder and order regions, respectively. \textbf{(D)} $\log_{10}$ disorder-to-order ratios of exchangeability coefficients. \textbf{(E-F)} Rate coefficients of disorder and order regions, respectively. The vertical and horizontal axes indicate the initial and target amino acids, respectively. \textbf{(G)} $\log_{10}$ disorder-to-order ratios of rate coefficients.}
\label{fig:substitution}
\end{figure}
